### 2016-12-28 2017mergingmerges/section/scrub.tex
there there

This local/global distinction is not a hard classification, as some systems fit somewhere in between.
For example, {\bf strymonas}~\cite{kiselyov2016stream} uses staged compilation for introspection of the code and to ensure appropriate inlining, but only performs producer-consumer fusion with a single local rule.

We make the following contributions:
\begin{itemize}
\item a process calculus for streaming programs (\S\ref{s:Process});
\item some common combinators implemented as processes (\S\ref{s:Combinators:Common});
\item and as an appendix more exotic combinators such as segmented operations (\S\ref{s:Combinators:Exotic});
\item an algorithm for fusing pairs of processes (\S\ref{s:Fusion});
\item and a formalisation and proof of soundness in Coq (\S\ref{s:Proofs});
\end{itemize}

@@

\section{Processes}
\label{s:Process}
We will start by looking at a combinator that increments each value.
Given an input stream @ins@, @increment ins@ returns a new stream with the incremented values.
The function @stream_1_1@ takes a process program with one pull input and one push output, and converts it to a stream program.

@@

\section{Combinators}

>>>>

This local/global distinction is not a hard classification, as some systems fit somewhere in between.
For example, {\bf strymonas}~\cite{kiselyov2016stream} uses staged compilation for introspection of the code and to ensure appropriate inlining, but seems to only perform producer-consumer fusion with a single local rule.

We make the following contributions:
\begin{itemize}
\item a process calculus for streaming programs (\S\ref{s:Processes});
\item some common combinators implemented as processes (\S\ref{s:Combinators:Common});
\item and as an appendix more exotic combinators such as segmented operations (\S\ref{s:Combinators:Exotic});
\item an algorithm for fusing pairs of processes (\S\ref{s:Fusion});
\item and a formalisation and proof of soundness in Coq (\S\ref{s:Proofs});
\end{itemize}

\input{section/XX-Processes.tex}

@@

\section{Processes}
\label{s:ProcessZZZ}

We will start by looking at a combinator that increments each value.
Given an input stream @ins@, @increment ins@ returns a new stream with the incremented values.
The function @stream_1_1@ takes a process program with one pull input and one push output, and converts it to a stream program.

@@

\section{Combinators}
\label{s:Combinators}
